Model of lens candidates from Space Warps CFHTLS

### 2016-07-13 paper2.tex
more words

% The list of authors, and the short list which is used in the headers.
% If you need two or more lines of authors, add an extra line using \newauthor
\author[R. K\"ung et al.]{
Rafael K\"ung,$^{1}$\thanks{E-mail: rafael.kueng@uzh.ch}
Prasenjit Saha,$^{1}$
Lucy Oswald$^{3}$
%and Fourth Author$^{4}$
\\
% List of institutions
$^{1}$Physik Institut, University of Zurich, Winterthurerstrasse XXX, Zurich 8057, Switzerland\\
$^{2}$Department, Institution, Street Address, City Postal Code, Country\\
$^{3}$Another Department, Different Institution, Street Address, City Postal Code, Country
%$^{4}$Another Department, Different Institution, Street Address, City Postal Code, Country
}

@@

\subsection{Parameterisation of pixel models} \label{subsec:parameter}
\todo{}
In order to fit the set of pixelated models to a single parameterised model, a program was written that took a parameterised function and subtracted from it the mean and the principle components of the data, which were calculated using classical Principle Component Analysis.
This created the residuals function.
The number of components defined as principle was varied to test how this affected the output, and it was found that using 5 principle components tended to give a reasonable approximation.
A masking function was added which selected only the data points that fell inside the image of the lens, and the principal components were clipped in order to keep the values inside the region of the ensemble of models.
Any value higher than the clip was set to be the clip value.
This was chosen to be 2.5 as, assuming that the data follows a Gaussian error distribution, almost all the values for the variance should lie between 2 and 3 standard deviations from the mean.
Minimising the residuals function produces the set of parameters that fit the parameterised function to the original pixelated ensemble most closely.
A least squares fit was used to perform this minimisation.
The parameterised model function was obtained from the gravitational potential of an isothermal ellipsoid mass distribution \cite{2001astro.ph..2341K}.
This model is frequently used to describe gravitational lenses as it tends to fit well with observations.
The isothermal ellipsoid model outputs three useful parameters: the radius of the Einstein ring, the ellipticity of the model and the angle of the ellipticity from the vertical, giving the orientation of the galaxy.
By applying this model to simulated lenses for which the values of these parameters were already known, it was possible to gain an estimate of the projected accuracy of the results, before applying the model to the candidate lensing galaxies.

@@

\begin{enumerate}
\item In the upper row we have first a cutout of the Space~Warps
  image, marked up with a spaghetti diagram.  There are four distinct
  lensed images, and the spaghetti diagram proposes that they are a
  minimum nearest to the lensing galaxy, a close minimum-saddle pair,
  and a minimum further away. In Table~\ref{tab:models} we refer to
  such configurations as `$1+2+1$'.
\item Alongside is a synthetic image produced by modelling.  In it,
  the fitted lensed images are shown in colour, while the lensing
  galaxy and extraneous objects have been reduced to grayscale.
  (Figure~\figref{synthmig} in \S~\ref{subsec:sourcefit} shows a
  synthetic image from another model of the same system.) These two
  panels are qualitative and display no units, and moreover, the
  mutual alignment of the two panels is only approximate.
\item The middle row shows contour maps from the model.  At middle
  left, we have the arrival-time surface.
\item At middle right we have the mass distribution in the usual
  dimensionless form $\kappa$.  Again, these two panels are mainly
  qualitative: both panels are spatially registered and centred on the
  density-peak of the lens, but no scales have been included.
\item The base row supplies spatial and mass scales.  The left panel
  shows the circularly-averaged $\kappa$ of the model ensemble, with
  increasing radius (in arcsec).  The four short vertical lines
  correspond to the minima and saddle points marked in the upper-left
  panel.  The effective Einstein radius is also shown.  As the radius
  scale indicates SW05 is comparatively large lens on the
  sky.\todo{Fix distance factor in $\kappa$.}
\item Lower right shows the total mass in the model against the
  estimated stellar mass, alongside the values for the whole sample.
  The lower-right shaded region is unphysical according to the
  stellar-population models, because it gives $M<\Mstel$. The
  upper-left shaded region is unphysical according to abundance
  matching, because it gives $M>\Mhalo$.  That is to say, the unshaded
  region is $0<\haloindex<1$.
\end{enumerate}

>>>>

% The list of authors, and the short list which is used in the headers.
% If you need two or more lines of authors, add an extra line using \newauthor

\author[K\"ung et al]{Rafael K\"ung,$^{1}$
Prasenjit Saha,$^{1}$
Ignacio Ferreras,$^{2}$
Elisabeth Baeten,$^{3}$
\newauthor
Jonathan Coles,$^{4}$
Claude Cornen,$^{3}$
Christine Macmillan,$^{3}$
Phil Marshall,$^{5}$ 
\newauthor
Anupreeta More,$^{6}$
Lucy Oswald$^{7}$
Aprajita Verma$^{8}$
and Julianne K. Wilcox$^{4}$
%
\\
%
$^{1}$Physik-Institut, University of Zurich, Winterthurerstrasse 190, 8057 Zurich, Switzerland\\
$^{2}$Mullard Space Science Laboratory, University College London, Holmbury St Mary, Dorking, Surrey RH5 6NT, UK\\
$^{3}$Zooniverse, c/o Astrophysics Department, University of Oxford, Oxford OX1 3RH, UK \\
$^{4}$Exascale Research Computing Lab, Campus Teratec, 2 Rue de la Piquetterie, 91680 Bruyeres-le-Chatel, France\\
$^{5}$Kavli Institute for Particle Astrophysics and Cosmology, Stanford University, 452 Lomita Mall, Stanford, CA 94035, USA\\
$^{6}$Kavli Institute for the Physics and Mathematics of the Universe, University of Tokyo, 5-1-5 Kashiwanoha, Kashiwa-shi 277-8583, Japan\\
$^{7}$Murray Edwards College, University of Cambridge, Cambridge CB3 0DF, UK\\
$^{8}$Sub-department of Astrophysics, University of Oxford, Denys Wilkinson Building, Keble Road, Oxford, OX1 3RH, UK\\
}

@@

\subsection{Parameterisation of pixel models} \label{subsec:parameter}
In order to fit the set of pixelated models to a single parameterised model, a program was written that took a parameterised function and subtracted from it the mean and the principle components of the data, which were calculated using classical Principle Component Analysis.
This created the residuals function.
The number of components defined as principle was varied to test how this affected the output, and it was found that using 5 principle components tended to give a reasonable approximation.
A masking function was added which selected only the data points that fell inside the image of the lens, and the principal components were clipped in order to keep the values inside the region of the ensemble of models.
Any value higher than the clip was set to be the clip value.
This was chosen to be 2.5 as, assuming that the data follows a Gaussian error distribution, almost all the values for the variance should lie between 2 and 3 standard deviations from the mean.
Minimising the residuals function produces the set of parameters that fit the parameterised function to the original pixelated ensemble most closely.
A least squares fit was used to perform this minimisation.
The parameterised model function was obtained from the gravitational potential of an isothermal ellipsoid mass distribution \cite{2001astro.ph..2341K}.
This model is frequently used to describe gravitational lenses as it tends to fit well with observations.
The isothermal ellipsoid model outputs three useful parameters: the radius of the Einstein ring, the ellipticity of the model and the angle of the ellipticity from the vertical, giving the orientation of the galaxy.
By applying this model to simulated lenses for which the values of these parameters were already known, it was possible to gain an estimate of the projected accuracy of the results, before applying the model to the candidate lensing galaxies.

@@

\begin{enumerate}
\item In the upper row we have first a cutout of the Space~Warps
  image, marked up with a spaghetti diagram.  There are four distinct
  lensed images, and the spaghetti diagram proposes that they are a
  minimum nearest to the lensing galaxy, a close minimum-saddle pair,
  and a minimum further away. In Table~\ref{tab:models} we refer to
  such configurations as `$1+2+1$'.
\item Alongside is a synthetic image produced by modelling.  In it,
  the fitted lensed images are shown in colour, while the lensing
  galaxy and extraneous objects have been reduced to grayscale.
  (Figure~\figref{synthimg} in \S~\ref{subsec:sourcefit} shows a
  synthetic image from another model of the same system.) These two
  panels are qualitative and display no units, and moreover, the
  mutual alignment of the two panels is only approximate.
\item The middle row shows contour maps from the model.  At middle
  left, we have the arrival-time surface.
\item At middle right we have the mass distribution in the usual
  dimensionless form $\kappa$.  Again, these two panels are mainly
  qualitative: both panels are spatially registered and centred on the
  density-peak of the lens, but no scales have been included.
\item The base row supplies spatial and mass scales.  The left panel
  shows the circularly-averaged $\kappa$ of the model ensemble, with
  increasing radius (in arcsec).  The four short vertical lines
  correspond to the minima and saddle points marked in the upper-left
  panel.  The effective Einstein radius is also shown.  As the radius
  scale indicates SW05 is comparatively large lens on the
  sky.\todo{Fix distance factor in $\kappa$.}
\item Lower right shows the total mass in the model against the
  estimated stellar mass, alongside the values for the whole sample.
  The lower-right shaded region is unphysical according to the
  stellar-population models, because it gives $M<\Mstel$. The
  upper-left shaded region is unphysical according to abundance
  matching, because it gives $M>\Mhalo$.  That is to say, the unshaded
  region is $0<\haloindex<1$.
\end{enumerate}
